The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-10-25 paper/ms.tex
editting the conclusions

In the case of homogeneously distributed sources, the changes in
line morphology are linked to the reduction in the average number of
scatterings. In the second part of Section \ref{sec:widthpeak} we show
that, as rotational velocity increases, a large fraction of photons
escape with less than $10$ scatterings. This makes highly improbable
that a photon's frequency can move away from the line's center.

@@

The changes in the number of scattering has a direct bearing on the
escape fraction. In Section \ref{}

Concerning the escape fraction under rotational effects on the
Ly$\alpha$ emission line, we found that the escape fraction increase
in about $20\%-30\%$for the homogeneous sphere model. While rotational
effects are negligible for the central models and the escape fraction
remains constant. Also the observer viewing angle have no effect in
the escape fraction neither for the homogeneous and central
models. Complementing this analysis we study the average number of
scatterings $<N_{scatt}>$ that photons perform before escaping of the
cloud taking into account rotational effects. The main result here is
for the homogeneous models for which as velocity increase photons
escape with about $\sim 39\%$  less scatterings than in the static
case.

>>>>

In the case of homogeneously distributed sources, the changes in
line morphology are linked to the reduction in the average number of
scatterings. In the second part of Section \ref{sec:widthpeak} we show
that, as rotational velocity increases, a large fraction of photons
escape with less than $10$ scatterings. On average there are $40\%$
less scatterings. This makes highly improbable that a photon's
frequency can move away from the line's center.

@@

These changes in the number of scatterings have a direct bearing on
the escape fraction in the presence of dust.  In Section
\ref{sec:escapefraction} we find that the escape fraction increases in
$20\%-30\%$ for the homogeneous source distribution. In the centrally
located emission, the rotational effects are negligible on the escape
fraction.
